### 2018-05-06 Paper/method.tex
..

>>>>

\begin{center}
\begin{tikzpicture}[node distance=1.5cm]

\node (start) [startstop] {Start};

\node (qoi) [io, below of=start,align=left] {Select an appropriate model output};

\draw [line] (start) -- (qoi);

\node (tol) [process, below of=qoi, text width=8em] {Set an initial tolerance, $\tau$};

\draw [line] (qoi) -- (tol);

\node (screen) [process, below of=tol, text width=9.5em] {Parameter Screening};

\draw [line] (tol) -- (screen);

\node (dr) [draw, diamond, aspect=2.0] {Is \\ Dimension-reduction \\ possible$?$};

\end{tikzpicture}
\end{center}
